---
title: "Palmerpenguins Findings"
author: "Tharuka"
date: "8/14/2021"
output: html_document
---

## Setting up the environment
Notes: Setting up the R environment by loading the 'tidyverse' and 'palmer penguins' packages

```{r loading packages}
library(ggplot2)
library(palmerpenguins)
```

## Visualizations
Here we will go through a series of visualizations

## Flipper and body mass in purple
Here we plot flipper length against body mass

```{r visualiza flipper and body mass in purple}
ggplot(data = penguins,aes(x=flipper_length_mm,y=body_mass_g)) +
  geom_point(color = "purple")

```

### Flipper and body mass by species
Here we plot flipper length against body mass and look at the breakdown by species

```{r species}
ggplot(data = penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape = species))

```

### Flipper and body mass by species and sex
Here we plot flipper length against body mass and look at the breakdown by species and sex

```{r species and sex}
ggplot(data = penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape = species))+
  facet_wrap(~sex)

```

